Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-09-17 article/manuscript.tex
format manuscript for new submission

\usepackage[none]{hyphenat} % to cancel auto-hyphenation
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

% \author[cp]{L.K.~Oshita\corref{cor1}}
% \cortext[cor1]{Corresponding author}
% \ead{l.oshita@yahoo.com}

% \author[ifixit]{A.~Pileggi}
% \author[cp]{S.~Pileggi}

% \address[cp]{Department of Statistics, California Polytechnic State University, San Luis Obispo, CA 93407, United States}
% \address[ifixit]{iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}

\begin{abstract} 
iFixit's community driven online question and answer forum (CQA), \textif{Answers}, contains an extensive amount of crowd-sourced information related specifically to device repair. This platform allows users to ask questions regarding repairs, and for both repair experts and everyday users to provide answers and feedback. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract}

\begin{keywords}
Cox regression \sep CQA forum \sep response time \sep survival analysis \sep survival probabilty 
\end{keywords}

>>>>

\usepackage[none]{hyphenat} % to cancel auto-hyphenation

\usepackage[numbers,sort&compress]{natbib} % for reference/citation formating
\bibpunct[, ]{[}{]}{,}{n}{,}{,}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{abstract} 
iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, contains an extensive amount of crowd-sourced information related specifically to device repair. This platform allows users to ask questions regarding repairs, and for both repair experts and everyday users to provide answers and feedback. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract}

\begin{keywords}
Cox regression; CQA forum; response time; survival analysis; survival probabilty 
\end{keywords}
